\chap{Acknowledgements}
%\addcontentsline{toc}{chapter}{Acknowledgements}

I first need to thank family for putting up with my academic saga. 
To my Mom and Dad, thanks so much for your unwavering support in helping me finish.
I am sure I would have quit long ago without your help. Your individual examples inspired much of who I am today.
To Kristi, thanks for being willing to step in to my life, even when it was hard, and guide me with your wisdom.
To my siblings, Michael, Zach, Ashley, and Caroline, I appreciate all of the teasing, without which I would not have developed the skin needed to survive this journey.
I also thank you for your friendship. I appreciate everything about being in your lives and look forward to our adventures together in the coming years.
To my grandparents, who gave advice and love and provided environments of peace for me to rest, thank you.

I also had the support of many JHU friends Alice Cocoros, Patrick Bryesse, Rachael Alexandroff, Kevin Nash, Dave Fehling, Keith Redwine, Erini Lambrides, Kirsten Hall, Dan Pfeffer, Tanvi Karwal (pew pew), Kim Berghaus, Charles Hussong, Nikhil Anand, Julian Munoz, Sean Cantrell, and many others who helped me along my way.
I would also like to acknowledge JoVone Pender, Keno Spruill, Matt Collinson, Charles Smith, Kim B. Miller, Debbie Camper and everyone at The Well who helped me when finishing seemed so impossibly hard. I appreciate you all for your love and support. 

I would like to specially recognize a few people. 
Raimon Jackson, thank you for choosing me as a brother and supporting me in my crazy ideas. Thank you for seeing my potential when I could not and fostering it. Thank you for supporting my family when it seemed like it would all fall apart. 
Matt Morris, thank you for your friendship and for all of the joys it has brought. I appreciate all of the time we have spent together and the times you have made my life possible. I hope to be able to return the favor one day.
Marc Osherson, thank you for all that you have given me. From day one, when I was touring JHU with you and the group, I knew we would be friends for life. From working out, discussing builds, drinking beer, and trying to solve the worlds problems, I have been and will remain eternally grateful for your friendship. So sayeth the wise Alaundo!

To my children, Helen and Alice, I hope you look back on my time in grad school with fond memories. I also hope you can forgive any bad temper I may or may not have developed while trying to finish this degree. I love you both very much and look forward to getting to know you as our family adventure continues. 

To Karen, my partner, my love, my light, the smartest person I know, the best mother I could ask for, thank you! Thank you for putting up with late nights, with me hunkering down and forgetting to look up, with commuting an hour and a half one way for 7 years, and for thinking I knew more than you about academia.
I am beyond grateful for the love you have showered me with and am excited to see where the rest of our journey together takes us. I am blessed to wake up with you everyday. Thank you!