\chap{Conclusions}
\label{chap:conclusion}

We have presented an analysis using the full Run 2 data probing several BSM models using the all hadronic channel of the $HH \rightarrow b\bar{b}b\bar{b}$ search.
We have also presented two extensions of this search that compliment its predictive abilities. 
As we have previously stated, there are many BSM models and trying to check every possible prediction is quite a large task.
The Higgs boson continues to be a unique lens into BSM models so there are many other extensions that have not been explored that should be in the future.
For example, there are other decay channels for a Higgs boson. A search where one of the Higgs bosons first decays to two W bosons is possible.
It is also possible to search for the CP-odd pseudo scalar, A, in a $Ha \rightarrow b\bar{b}b\bar{b}$ analysis.
The search, $aa \rightarrow b\bar{b}b\bar{b}$, has recently been completed so $Ha \rightarrow b\bar{b}b\bar{b}$ would compliment the main analysis and the previously mentioned one nicely.

The main search of this thesis is not complete however. 
In Run 3 it is possible that enough data will be taken to directly measure the Higgs boson self coupling with the $HH \rightarrow b\bar{b}b\bar{b}$ search.
This measurement is a good test of the SM in conjunction with the quartic coupling measurement that was presented in Section \ref{s:vbf}.
One of the basic principles of science is to continuously verify that your theory is accurate.
This accomplishes two main tasks. The first is it serves to push science to do an even more accurate job of describing our physical universe.
The second is it provides the chief avenue for discovery as discrepancies between theory and experiment can sometimes widen into chasms of new understanding.
In this approach, science never rests.
